## This is the lab for week 2 
## Add working R code in between the questions
## The functions refer to the sections in https://rspatial.org/intr/

## Functions

## 1) Write a function 'f' that behaves like this:
## > f('Jim')
## [1] "hello Jim, how are you?"
##HINT: you will need to use the paste() function within your new function

```{r}
f <- function(name) {
  paste("hello", name, "how are you?")
}
f('Jim')
f
```
## 2) Write a function 'sumOfSquares' that behaves like this:


## > d <- c(1,5,2,4,6,2,4,5)
## > sumOfSquares(d)
## [1] 21.875
```{r}
sumOfSquares <- function(d) {
  d <- c(1,5,2,4,6,2,4,5)
  m <-sum(d)/length(d)
  sub <-d-m
  t <-sum(sub^2)
  return(t)
}
d <- c(1,5,2,4,6,2,4,5)
sumOfSquares(d)
```

# To compute the "sum of squares", subtract the mean value of all numbers from each number. 
# Square these numbers and sum them
# (bonus: make a variant that can handle NAs)


## Flow Control

## 4) Write a for loop that adds the numbers 1 to 10
##HINT: you will need one variable that loops through the numbers 1 to 10 and one that keeps count through each loop
```{r}
x <- (1:10)
y <- 0

for (i in 1:length(x)) {
  y<- y+x[i]
  print(y)
}

y
```
## 5) Write a for loop that adds the odd numbers between 1 and 10 
```{r}
y<- 0
x<- seq(from=1, to=9, by=2)
for (i in x) {
  y<- y +i
}
print(y)
```
